Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Community Detection and Parameter Estimation

### 2021-03-23 summary.Rmd
fixed ssc scaling

\begin{algorithm}[t]
  \DontPrintSemicolon
  \SetAlgoLined
  \caption{Sparse Subspace Clustering using LASSO \cite{pmlr-v28-wang13}.}
  \KwData{Adjacency matrix $A$, number of communities $K$, 
  hyperparameter $\lambda$}
  \KwResult{Community assignments $1, ..., K$}
    Find $V$, the matrix of eigenvectors of $A$ 
    corresponding to the $K (K + 1) / 2$ most positive 
    and the $K (K - 1) / 2$ most negative eigenvalues.\;
    \For {$i = 1, ..., n$} {
      Assign $v_i^\top$ as the $i^{th}$ row of $V$. 
      Assign $V_{-i} = \begin{bmatrix} 
      v_1 & \cdots & v_{i-1} & v_{i+1} & \cdots & v_n \end{bmatrix}^\top$.\;
      Solve the LASSO problem 
      $c_i = \arg\min_{\beta} 
      \frac{1}{2} ||v_i - V_{-i} \beta||_2^2 + \lambda ||\beta||_1$.\;
      Assign $\tilde{c}_i = \begin{bmatrix} 
      c_i^{(1)} & \cdots & c_i^{(i-1)} & 0 & c_i^{(i)} & \cdots & c_i^{(n-1)}
      \end{bmatrix}^\top$ such that the superscript is the index of 
      $\tilde{c}_i$.\;
    }
    Assign 
    $C = \begin{bmatrix} \tilde{c}_1 & \cdots & \tilde{c}_n \end{bmatrix}$.\;
    Compute the affinity matrix $B = |C| + |C^\top|$.\;
    Construct graph $G$ using $B$ as its similarity matrix.\;
    Partition $G$ into $K$ disconnected subgraphs (e.g., using edge 
    thresholding or spectral clustering).\;
    Map each partition to the community labels $1, ..., K$. 
\end{algorithm}

\begin{theorem}
\label{theorem5}
Let $P_n$ describe the edge probability matrix of the PABM with 
$n$ vertices, and let $A_n \sim \Bernoulli(P_n)$.  Let $\hat{V}_n$ be the 
matrix of eigenvectors of $A_n$ corresponding to the $K (K + 1) / 2$ most
positive and $K (K - 1) / 2$ most negative eigenvalues. Then 
$\exists \lambda > 0$ such that $\hat{B}_n$, the affinity matrix
outputted by SSC using $\hat{V}_n$ and $\lambda$, has $ij^{th}$ entry
$\hat{B}_n^{(ij)} \stackrel{a.s.}{\to} 0$ $\forall i, j$ in different 
communities. 
\end{theorem}

>>>>

\begin{algorithm}[t]
  \DontPrintSemicolon
  \SetAlgoLined
  \caption{Sparse Subspace Clustering using LASSO \cite{pmlr-v28-wang13}.}
  \KwData{Adjacency matrix $A$, number of communities $K$, 
  hyperparameter $\lambda$}
  \KwResult{Community assignments $1, ..., K$}
    Find $V$, the matrix of eigenvectors of $A$ 
    corresponding to the $K (K + 1) / 2$ most positive 
    and the $K (K - 1) / 2$ most negative eigenvalues.\;
    \For {$i = 1, ..., n$} {
      Assign $v_i^\top$ as the $i^{th}$ row of $V$. 
      Assign $V_{-i} = \begin{bmatrix} 
      v_1 & \cdots & v_{i-1} & v_{i+1} & \cdots & v_n \end{bmatrix}^\top$.\;
      Solve the LASSO problem 
      $c_i = \arg\min_{\beta} 
      \frac{1}{2} ||v_i - V_{-i} \beta||_2^2 + \lambda ||\beta||_1$.\;
      Assign $\tilde{c}_i = \begin{bmatrix} 
      c_i^{(1)} & \cdots & c_i^{(i-1)} & 0 & c_i^{(i)} & \cdots & c_i^{(n-1)}
      \end{bmatrix}^\top$ such that the superscript is the index of 
      $\tilde{c}_i$.\;
    }
    Assign 
    $C = \begin{bmatrix} \tilde{c}_1 & \cdots & \tilde{c}_n \end{bmatrix}$.\;
    Compute the affinity matrix $B = \sqrt{n} (|C| + |C^\top|)$.\;
    Construct graph $G$ using $B$ as its similarity matrix.\;
    Partition $G$ into $K$ disconnected subgraphs (e.g., using edge 
    thresholding or spectral clustering).\;
    Map each partition to the community labels $1, ..., K$. 
\end{algorithm}

\begin{theorem}
\label{theorem5}
Let $P_n$ describe the edge probability matrix of the PABM with 
$n$ vertices, and let $A_n \sim \Bernoulli(P_n)$.  Let $\hat{V}_n$ be the 
matrix of eigenvectors of $A_n$ corresponding to the $K (K + 1) / 2$ most
positive and $K (K - 1) / 2$ most negative eigenvalues. Then 
$\exists \lambda > 0$ such that as $n \to \infty$, $\hat{V}_n$ obeys the 
subspace detection property with probability 1.
\end{theorem}
